Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Related work

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then
weakened forms of degree and path based filterings are still effective in pruning the initial search
space and in providing additional constraints respectively. We then show that combining these
techniques leads to a practical algorithm which can scale to work with the families of graphs
commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, we
can close a substantial portion of the instances, and in many more cases, we can at least obtain an
upper bound. This is a significant improvement over state of the art maximum common subgraph
solvers, which cannot even fit many of these instances in RAM. Finally, we show that iteratively
increasing $k$ gives a competitive algorithm for the maximum common induced subgraph problem.

>>>>

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target. (This in some ways resembles the approximate subgraph matching model
of \citet{DBLP:conf/cp/ZampelliDD05}, although we allow any vertex to be removed.) We show that if
$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
filterings are still effective in pruning the initial search space and in providing additional
constraints respectively. We then show that combining these techniques leads to a practical
algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
algorithm for the maximum common induced subgraph problem.
